SSA based global code motion of identical computations

### 2017-04-17 paper.tex
spills
rebase

Loads are hoisted the most followed by scalars, stores and calls in decreasing
order.  This was the common trend in all our experiments. One reason why loads
are hoisted the most is the early execution of this pass (before mem2reg) in the
\LLVM{} pass pipeline. Passes like mem2reg, instcombine might actually remove
those loads so this order may change should this pass be scheduled later. The number
of instructions sunk is very less because \LLVM{} has a code sinking pass inside SimplifyCFG
which is run before the global code-motion and sinks some instructions. Another reason is
that instructions for which dependencies are not directly available in the successor is
not sunk for now. Sinking those instructions would require a look ahead on the sinkability
of the dependencies. We plan to implement this in near future.

>>>>

Loads are hoisted the most followed by scalars, stores and calls in decreasing
order.  This was the common trend in all our experiments. One reason why loads
are hoisted the most is the early execution of this pass (before mem2reg) in the
\LLVM{} pass pipeline. Passes like mem2reg, instcombine might actually remove
those loads so this order may change should this pass be scheduled later.
